A systematic search for transiting planets using \KT

### 2015-02-05 ms.tex
discussion

\acknowledgments
It is a pleasure to thank
\ldots\
for helpful contributions to the ideas and code presented here.
This project was partially supported by the NSF (grant AST-0908357), NASA
(grant NNX08AJ48G), and the Moore--Sloan Data Science Environment at NYU.
This research made use of the NASA \project{Astrophysics Data System}.

>>>>

\paragraph{Maybe this goes in results}

We include posterior distributions of planet candidate properties, available at
\dfmtodo{thisurl}. 
These distributions are specifically \emph{NOT} marginalized over stellar 
properties.
In this work, we are agnostic about fundamental properties of the host star.
In fact, the only assumptions we make are that the star targeted by the \KT\ 
team is truly the planet host, and that there is no dilution by other stars in
any aperture. 
As a result, these posterior distributions reflect the maximum possible 
uncertainty in parameters such as the planet radius which depend sensitively 
on properties of the host star.

To use our distributions to characterize individual systems, one

\acknowledgments
It is a pleasure to thank
\ldots\
for helpful contributions to the ideas and code presented here.
This project was partially supported by the NSF (grant AST-0908357), NASA
(grant NNX08AJ48G), and the Moore--Sloan Data Science Environment at NYU.
B.T.M. is supported by the National Science Foundation Graduate Research 
Fellowship under Grant No. DGE‐1144469.
This research made use of the NASA \project{Astrophysics Data System}.
